%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Siddhanathan}{Shanmugam}{
  \urlstyle{same}\href{https://github.com/siddhanathan}{github.com/siddhanathan} \\
  \href{mailto:ss3774@drexel.edu}{ss3774@drexel.edu} | +1 (215) 730-5983
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Drexel University}
\descript{BS in Computer Science}
\location{June 2018 | Philadelphia, PA}
Pennoni Honors College \\
Dean's List
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\subsection{Programming}
\location{Preferred:}
Haskell \textbullet{} Rust \textbullet{} Go \\
\location{Comfortable with:}
C \textbullet{} Assembly \textbullet{} Scala \textbullet{} SQL \\
Java \textbullet{} HTML \textbullet CSS \textbullet{} Javascript \\
VHDL \\
\location{Familiar:}
OCaml \textbullet{} Clojure \textbullet{} \LaTeX\ \\ 

\sectionsep
\subsection{Tools}
Vi \textbullet{} Awk \textbullet{} ZSH \textbullet{} Bash \\
tmux \textbullet{} Mosh \textbullet{} Python
\sectionsep

\subsection{Hardware}
Soldering \textbullet{} Arduino \textbullet{} PCB Design
\sectionsep

\subsection{Theory}
Operating Systems \\
Compiler Design \\
Functional Programming \\
Communication Systems \\
Digital Signal Processing \\
Control Systems \\
Computer Networks \\
Parallel \& Concurrent Programming \\
Unix Tools and Scripting
\sectionsep

\subsection{Language}
English \textbullet{} Hindi \textbullet{} Tamil

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CONTRIBUTIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Contributions}
\subsection{Open Source}
Glassgow Haskell Compiler \\
Yi Text Editor \\
Ubuntu \\
Sympy \\
NixOS \\
Vimgolf
\sectionsep

\subsection{College}
DragonHacks \\
Drexel IEEE \\
Drexel Linux Users Group \\
Drexel Hyperloop
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Drexel University}
\descript{| Research Assistant }
\location{September 2015 - March 2016 | Philadelphia, PA}
\sectionsep

\runsubsection{CDM Inc.}
\descript{| Data Analyst }
\location{September 2014 – March 2015 | Philadelphia, PA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Wrote parsers for text and binary formats.
\item Setup backup servers for Amazon AWS instances.
\item Wrote statistical modelling applications with a web based user interface.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Ziria}
\descript{| Research Assistant }
\location{April 2015 - Present | Philadelphia, PA}
\begin{tightemize}
\item Worked on the Ziria project under the mentorship of Geoffrey Mainland.
\item Ported the compiler toolchain to Linux.
\item Profiled the C-backend for performance bottlenecks.
\item Optimized slow sections of the C-backend.
\item Wrote tools to auto generate performance charts.
\item Ported DSP algorithms from C to high-level PHY descriptions in Ziria.
\item Worked on a VHDL backend for an OFDM implementation.
\end{tightemize}
\sectionsep

\runsubsection{Oratio}
\descript{| Researcher}
\location{November 2015 – Present | Philadelphia, PA}
Worked on an algorithm for objectively classifying quality of speech in real time.
\sectionsep

\runsubsection{Hyperloop}
\descript{| Control Systems Engineer }
\location{September 2015 – Present | Philadelphia, PA}
Proposed a revolutionary approach for controls to SpaceX engineers.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\subsection{Paper Touché}
\location{ Hacking Audio and Music Research, Philly 2014 }
A touch capacitive paper based musical synthesizer focused on
Human Computer Interaction. Used a touch-based interface made using
paper and graphite.
\sectionsep

\subsection{cvRecognition}
\location{ \#Hack4Access, Philly 2014 }
Context aware face recognition for Android. Also includes traffic light detection.
Initially aimed towards helping people with memory loss issues, but later tweaked
to help people who are visually impaired as well.
\sectionsep

\subsection{Dragon TMS}
\location{ Philly Codefest 2015 }
An automatic class schedule generating application for students of Drexel University.
Capable of avoiding time conflicts, and ranking schedules based on user preferences.
\sectionsep

\subsection{SWMMoutGetMB}
\location{ Philly 2015 }
A parser for US EPA SWMM 5 binary .OUT files, with an option to export CSV data.
The program has seen real world usage by multiple governments across the world.
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
