\cvsection{Experience}
\begin{cventries}
  \cventry
    {Research Assistant}
    {Geoffrey Mainland, Drexel University}
    {Philadelphia, U.S.A.}
    {Sep. 2015 - PRESENT}
    {
      \begin{cvitems}
        \item {Worked on Ziria, a programming language and compiler for low-level bitstream processing.}
        \item {Ported the compiler-toolchain to Linux.}
        \item {Profiled the C-backend for performance bottlenecks, and optimized slow sections of the C-backend.}
        \item {Wrote tools to auto-generate performance charts.}
        \item {Worked on an OFDM implementation which uses a VHDL-backend.}
      \end{cvitems}
    }
  \cventry
    {Data Analyst}
    {CDM Inc.}
    {Philadelphia, U.S.A.}
    {Sep. 2014 - Apr. 2015}
    {
      \begin{cvitems}
        \item {Wrote parsers for binary file formats dealing with big data.}
        \item {Used data analytics to help engineers understand their data.}
        \item {Developed and deployed web applications which made repeated data analysis easier.}
      \end{cvitems}
    }
  \cventry
    {Volunteer}
    {Canonical Ltd.}
    {London, U.K.}
    {Sep. 2010 - Sep. 2014}
    {
      \begin{cvitems}
        \item {Tested unstable packages and reported bugs for QA/QC.}
      \end{cvitems}
    }
  \cventry
    {Mentee}
    {Sympy Development Team}
    {Google Code-In}
    {Sep. 2011 - Feb. 2012}
    {
      \begin{cvitems}
        \item {Used Sphinx to auto-document Sympy source code.}
      \end{cvitems}
    }
\end{cventries}
